---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(jsonlite)
```

# googleErrorReportingR

<!-- badges: start -->
<!-- badges: end -->

# googleErrorReportingR
This is an R wrapper for the Google Cloud Platform Error Reporting API. I uses the Error Reporting API as defined in the [projects.events.report](https://cloud.google.com/error-reporting/reference/rest/v1beta1/projects.events/report) method.

Using the Google OAuth 2.0 authentication is on the wishlisht. The current version only authenticates using an API key so that we can have a call like:

    report_error(api_key, message)

and have this work consistently.

## Installation

You can install the development version of googleErrorReportingR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ixpantia/googleErrorReportingR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(googleErrorReportingR)

api_key <- Sys.getenv("API_KEY")

message <- list()
message$message <- "My message"
message$serviceContext$service <- "Some service"
message$serviceContext$service <- "mi-servicio"
message$context$reportLocation$lineNumber <- 10
message$context$reportLocation$functionName <- "miFuncion"
message$context$reportLocation$filePath <- "miarchivo.R"
```

Note that we have a fully formated JSON even message by using the list

```{r}
toJSON(message, auto_unbox = TRUE, pretty = TRUE )
```

And we can now send the report to our Google project.

```{r write out error report}
project_id <- "infraestructura-pruebas"

googleErrorReportingR::report_error(project_id,
                                    api_key,
                                    message)
```
