---
title: "error_reporting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{error_reporting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(googleErrorReportingR)
```

## Context

Having a central place where we can gather errors and warnings from our R code
is particularly relevant when we have deployed our code and have users actively
making use of the services we have set up. Users will not always bother to
report an error, and in the case of API's where the users are other machines,
this is even more unlikely.

IaaS platforms such as Google Cloud Platform typically have monitoring and
loggin services available. This package offers you convenience wrapper around
the `projects.events` API to report errors of your services.

## Message format

For some language Google has implemented functionality to capture the stacktrace
and use that as a basis for a report. When using R code we need to create the
erorr message, but note that we can still include dynamic content. For instance,
we can setup a `tryCatch()` call and output the `e` (error) to a Error Reporting
call.

              message = "Error description",
              # service
              service = "My Service",
              version = "0.0.1",
              # context
              method = "GET",
              url = "https://example.com",
              userAgent = "",
              referrer = "",
              responseStatusCode = "500",
              remoteIp = "192.178.0.0.1",
              user = "UserID",
              #reportLocation
              filepath

 note we leave the following items out for the following reasons
- "eventTime": string, -- this has to be formated to Zulu, this is possible,
  but much easier to just rely on the event time. If you do want to include
  time note that you will need to use the Zulu format requried by Google. For example

```{r, eval=FALSE}
message$eventTime <- format(lubridate::now(), "%Y-%m-%dT%H:%M:%SZ")
```

 - "@type": string - Optional. For information on this field, see [Specify @type](https://cloud.google.com/error-reporting/docs/formatting-error-messages#@type).
